R Notebook

### 2022-04-27 R/HumanDeaminationAnalysis.rmd
Update HumanDeaminationAnalysis.rmd

```{r CPD_mismatch_pos_frequency}
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], includedTypes = c("C>T"),
                                    title = paste("CPD", names(CPDMismatchData)[i], 
                                                  names(CPDMismatchData[[i]])[j], "C>T Mismatch Positions"),
                                    posType = FIVE_PRIME)
    plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], omittedTypes = c("C>T"),
                                    title = paste("CPD", names(CPDMismatchData)[i], 
                                                  names(CPDMismatchData[[i]])[j], "!C>T Mismatch Positions"))
  }
}
```

>>>>

```{r CPD_mismatch_pos_frequency}
for (i in 1:length(CPDMismatchData)) {
  for (j in 1:length(CPDMismatchData[[i]])) {
    plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], includedTypes = c("C>T"),
                                    title = paste("CPD", names(CPDMismatchData)[i], 
                                                  names(CPDMismatchData[[i]])[j], "C>T Mismatch Positions"))
    plotMismatchPositionFrequencies(CPDMismatchData[[i]][[j]], omittedTypes = c("C>T"),
                                    title = paste("CPD", names(CPDMismatchData)[i], 
                                                  names(CPDMismatchData[[i]])[j], "!C>T Mismatch Positions"))
  }
}
```
